### 2021-12-12 thesis/tex/conclusion.tex
update

\chapter{Conclusion}\label{ch:conc}
We were able to simulate the IceCube experiment with 86 strings, with our $3+0$ hypothesis shown against the IceCube Monte Carlo in Fig~\ref{fig:IC_MC_norm}. 
We normalized against the Monte Carlo, and produced the exclusion contour between the sterile neutrino parameters $\dm[41]$ and $\theta_[24]$ in Fig~\ref{fig:error_tuning}.
We found that the data is consistent with the $3+0$ hypothesis, with deviations up to 6\% at $\SI{10}{\TeV}$.
We also investigated the case when $\theta_{24} = \theta{34}$, and which produced an identical exclusion contour as in the case with $\theta_{34}=0$. This 
observation makes us conclude that IceCube is currently insensitive to any impact of $\theta_{34}$, with track events alone. However,
when opening up the $\tau$ channel by allowing $\theta_{34} \neq 0$, it is possible that with an inclusion of cascade events from $\nt$, IceCube could be able to observe 
an impact of $\theta_{34}$.

% TODO Conclusion:
% We produced the conclusion plots, and ic is insensitive to any impact if th34.
% NSI: which detector is more sensitive? Add paragraph on what parameters that PINGU can measure (in future tense). Write what constrain which parameters?
% Include effect on system uncertainty on PINGU. Compare with other measurements. Write from fig 5.7 that let Eem are anti-correlated, while no significant correlation can be seen from emt-emt, emt-eet.
% Reference papers on PINGU, NSI. And NSI from Llong baseline experiments. Include reference to DUNE from ESS paper with S+T+M.

>>>>

\chapter{Conclusion}\label{ch:conc}
We were able to simulate the IceCube experiment with 86 strings, with our $3+0$ hypothesis shown against the IceCube Monte Carlo in Fig~\ref{fig:IC_MC_norm}. 
We normalized against the Monte Carlo, and produced the exclusion contour between the sterile neutrino parameters $\dm[41]$ and $\theta_[24]$ in Fig~\ref{fig:error_tuning}.
We found that the data is consistent with the $3+0$ hypothesis, with deviations up to 6\% at $\SI{10}{\TeV}$.
Our best-fit parameters were found to be$\dm[41] = \SI{0.01}{\eV^2}$ and $\theta_{24} = 0.67$ ($\sin^22\theta_{24} = 0.95$) at 
a p-value of $33\%$.
We also investigated the case when $\theta_{24} = \theta{34}$, and which produced an identical exclusion contour as in the case with $\theta_{34}=0$. This 
observation makes us conclude that IceCube is currently insensitive to any impact of $\theta_{34}$, with track events alone. However,
when opening up the $\tau$ channel by allowing $\theta_{34} \neq 0$, it is possible that with an inclusion of cascade events from $\nt$, IceCube could be able to observe 
an impact of $\theta_{34}$.

In our second part of the work, we put the sterile neutrino completely aside, and turned our focus to non-standard interactions. 
We included DeepCore in order to both lower the energy range of the data, but also to include cascade events in this range. 
Additionally, we simulated a proposed upgrade to DeepCore, PINGU, and produced data for it assuming a standard $3+0$ hypothesis with parameters from\cite{nufit}.
We saw that, on a probability level, in the high energy region of IceCube, NSI effects other than those stemming from $\emt$ are not apparent.
Moreover, we saw in the $\Pme$ shown in Fig~\ref{fig:eem_eet_prob} that we could expect a correlation between $\eem$ and $\eet$ in the single-digit \si{\GeV} range.
We also saw that $\emt$ effects were visible on probability level in both the \si{\GeV} and \si{\TeV} regions, making us hope to constrain $\emt$ further by 
a joint analysis.
In Fig~\ref{fig:event_pulls}, we saw that we can expect PINGU to be more sensitive to NSI effects than DeepCore, with $\emt$ effects being the weakest 
due to their low effect on all probability channels in the \si{\GeV} range.

% TODO Conclusion:
% NSI: which detector is more sensitive? Add paragraph on what parameters that PINGU can measure (in future tense). Write what constrain which parameters?
% Include effect on system uncertainty on PINGU. Compare with other measurements. Write from fig 5.7 that let Eem are anti-correlated, while no significant correlation can be seen from emt-emt, emt-eet.
% Reference papers on PINGU, NSI. And NSI from Llong baseline experiments. Include reference to DUNE from ESS paper with S+T+M.

### 2021-12-12 thesis/tex/nsiTheory.tex
update

@@

Fig.~\ref{fig:Pee_eet_probs} shows the electron neutrino and antineutrino survival probabilities, and here we see
a clear difference when turning on $\eet$.

\begin{figure}
    \begin{center}
        \includegraphics[width=0.9\textwidth]{figures/Pee_eet_probs.pdf}
        \caption{Electron neutrino and antineutrino survival probabilities for
        $\ztrue = -1$ when $\eet = 0.2$. All other NSI parameters are fixed to zero. Compared to the $\nm$ and $\anm$ plots, here we see a strong difference across the whole energy range.}
        \label{fig:Pee_eet_probs}
    \end{center}
\end{figure}

>>>>

Fig.~\ref{fig:Pee_eet_probs} shows the electron neutrino and antineutrino survival probabilities, and here we see
a clear signal when turning on $\eet$.

\begin{figure}
    \begin{center}
        \includegraphics[width=0.9\textwidth]{figures/Pee_eet_probs.pdf}
        \caption{Electron neutrino and antineutrino survival probabilities for
        $\ztrue = -1$ when $\eet = 0.2$. All other NSI parameters are fixed to zero. Here we see a strong difference across the whole energy range, in contrast to the $\nm$ and $\anm$ plots in Fig~\ref{eem_eet_probs}.}
        \label{fig:Pee_eet_probs}
    \end{center}
\end{figure}

@@

### 2021-12-12 thesis/tex/sterileResults.tex
update

By tuning the scaling $f$ of the uncorrelated systematic error, we can shift the contour. We extract the contour from the 
IceCube sterile neutrino analysis~\cite{IC2020}, and compare in Fig.~\ref{fig:error_tuning}. We see that the contour in the 
higher $\dm[41]$ region above \SI{1}{\eV\squared} is very sensitive to the tuning, while the lower region between \SIrange[]{1e-1}{1}{\eV\squared}
remains fixed. In both cases, we obtain best-fit values of $\dm[41] = \SI{0.01}{\eV^2}$ and $\theta_{24} = 0.67$
\begin{figure}
    \centering
    \includegraphics[scale=0.58]{figures/s24_error_tuning.pdf}
    \caption{The 90\% CL contour with two different systematic error scalings, compared 
    with the official IceCube result from~\cite{IC2020}.}\label{fig:error_tuning}
\end{figure}

We now in Fig.~\ref{fig:final_rate_plot} plot the best-fit 3+1 hypothesis with the data from Fig.~\ref{fig:IC_rates}, to finally see how the best 
3+1 hypothesis compares to data.
\begin{figure}
    \centering
    \includegraphics[width=1\textwidth]{figures/final_rate_plot.pdf}
    \caption{The predicted binned event count assuming our best-fit 3+1 hypothesis in blue, compared with the 
    null 3+0 hypothesis in red and data points in black.}\label{fig:final_rate_plot}
\end{figure}

>>>>

By tuning the scaling $f$ of the uncorrelated systematic error, we can shift the contour. We extract the contour from the 
IceCube sterile neutrino analysis~\cite{IC2020}, and compare in Fig.~\ref{fig:error_tuning}. We see that the contour in the 
higher $\dm[41]$ region above \SI{1}{\eV\squared} is very sensitive to the tuning, while the lower region between \SIrange[]{1e-1}{1}{\eV\squared}
remains fixed. In both cases, we obtain best-fit values of $\dm[41] = \SI{0.01}{\eV^2}$ and $\theta_{24} = 0.67$ ($\sin^22\theta_{24} = 0.95$) at 
a p-value of $33\%$.
\begin{figure}
    \centering
    \includegraphics[scale=0.58]{figures/s24_error_tuning.pdf}
    \caption{The 90\% CL contour with two different systematic error scalings, compared 
    with the official IceCube result from~\cite{IC2020}.}\label{fig:error_tuning}
\end{figure}

We now in Fig.~\ref{fig:final_rate_plot} plot the best-fit 3+1 hypothesis with the data from Fig.~\ref{fig:IC_rates}, to finally see how the best 
3+1 hypothesis compares to data.
\begin{figure}
    \centering
    \includegraphics[width=1\textwidth]{figures/final_rate_plot.pdf}
    \caption{The predicted binned event count assuming our best-fit 3+1 hypothesis in blue with $\dm[41] = \SI{0.01}{\eV^2}$ and $\theta_{24} = 0.67$, compared with the 
    null 3+0 hypothesis in red and data points from ~\cite{IC2020} in black.}\label{fig:final_rate_plot}
\end{figure}
